A Fully Abstract Game Semantics for Countable Nondeterminism

### 2018-01-29 cones/paper/cones.tex
Changed some things.

The language that we will be modelling is the language Idealized Algol \cite{SamsonGuyIAPassive}, extended with an additional constant $\wn$ representing countable nondeterminism.  
This is similar to the approach adopted in \cite{mcCHFiniteND}, which extends Idealized Algol with \emph{finite} nondeterminism.  
The types of the language are defined inductively as follows:
\[
  T \Coloneqq \nat \mid \com \mid \Var \mid T \to T\,.
  \]
Meanwhile, the terms are those given in \cite{SamsonGuyIAPassive}, together with the nondeterministic choice:
\begin{IEEEeqnarray*}{RCL}
  M & \Coloneqq & x \mid \lambda x . M \mid M\;M \mid \Y_T M \mid \\
  && \n \mid \skipp \mid \suc M \mid \pred M \mid \\
  && \IfO M\;M\;M \mid M;M \mid \\
  && M \coloneqq M \mid \deref M \mid \\
  && \neww_T\;M \mid \mkvar M\;M \mid \wn\,.
\end{IEEEeqnarray*}

@@

The value forms in the language are given by
\[
  V \Coloneqq \skipp \mid \n \mid \lambda x.M \mid v \mid \mkvar
  \]
We define predicates $M \converges V$ ($M$ may converge to $V$) and $M\mustconverge$ ($M$ must converge) inductively to give a big-step operational semantics for our language.  
We give a selection of the appropriate rules in Figure \ref{fig:ia-os}; this presentation is almost identical to that given in \cite{mcCHFiniteND}, with a slightly different rule for the countable nondeterminism.  
In each rule, $\ia{s}{M}$ is a \emph{configuration} of the language, where $M$ is a term, and $s$ is a \emph{store}; i.e., a function from the set of variables free in $M$ to the set of natural numbers.  
If $s$ is a store and $v$ a variable, we write $\stup s v n$ for the state formed by updating the value of the variable $v$ to $n$.

>>>>

The language that we will be modelling is Idealized Algol \cite{SamsonGuyIAPassive} extended with an additional constant $\wn$ representing countable nondeterminism.  
This is similar to the approach adopted in \cite{mcCHFiniteND}, which extends Idealized Algol with \emph{finite} nondeterminism.  
The types of the language are defined inductively as follows:
\[
  T \Coloneqq \nat \mid \com \mid \Var \mid T \to T\,.
  \]
Meanwhile, the terms are those given in \cite{SamsonGuyIAPassive}, together with the nondeterministic choice:
\begin{IEEEeqnarray*}{RCL}
  M & \Coloneqq & x \mid \lambda x . M \mid M\;M \mid \Y_T M \mid \\
  && \n \mid \skipp \mid \suc M \mid \pred M \mid \\
  && \IfO M\;M\;M \mid M;M \mid \\
  && M \coloneqq M \mid \deref M \mid \\
  && \neww_T\;M \mid \mkvar M\;M \mid \wn\,.
\end{IEEEeqnarray*}

@@

The value forms in the language are given by
\[
  V \Coloneqq \skipp \mid \n \mid \lambda x.M \mid v \mid \mkvar
  \]
We define predicates $M \converges V$ ($M$ may converge to $V$) and $M\mustconverge$ ($M$ must converge) inductively to give a big-step operational semantics for our language.  
We give a selection of the appropriate rules in Figure \ref{fig:ia-os}; this presentation is almost identical to that given in \cite{mcCHFiniteND}, with a rule for countable nondeterminism replacing their rule for finite nondeterminism.  
In each rule, $\ia{s}{M}$ is a \emph{configuration} of the language, where $M$ is a term, and $s$ is a \emph{store}; i.e., a function from the set of variables free in $M$ to the set of natural numbers.  
If $s$ is a store and $v$ a variable, we write $\stup s v n$ for the state formed by updating the value of the variable $v$ to $n$.
